Applications of the Fresnel Integrals

### 2019-03-17 draft.tex
Fresnel diffraction

\subsection{Fresnel Diffraction}
\cite{BH12}
Electromagnetic field intensity
in the physics of diffraction

In optics, the illuminationintensity at a point behind a slit is computed from the distance between two points on the Euler spiral.

\subsection{Railway  Construction}

>>>>

\subsection{Fresnel Diffraction}
\defbf\E{E}
\defbf\B{B}
\begin{figure}[h!]
	\centering
	\includegraphics[width=0.5\textwidth]{opticalSetting.png} \\
	% (2) \includegraphics[width=0.5\textwidth]{opticalParameters.png}
	\label{f:FresnelDiffraction}
	\caption{Fresnel diffraction after \cite[ch.~8.1]{Zim08}. Incoming parallel light waves from the left.  An aperture S' and an observation screen on the right in distance $D$.}
\end{figure}
According to \cite[ch.~7]{Zim08} the complexified electric field strength $\E$ at a point $P$ on the observation screen of a plane electromagnetic wave that went through an aperture $S'$ computes as
\[  \E(P) = \B\iint  \frac1\rho \exp\left(\si(k\rho-\omega t)\right) \d{S'}
\] where $\B$ determines the amplitude of the incoming wave,\\ $\rho=\sqrt{(x-x')^2+(y-y')^2+D^2}$ is the distance of the aperture point $S'$ from the observation point $P$.  $k=\omega/c$ is the wave number, $\omega$ the frequency of the incoming monochromatic wave and $c>0$ the speed of light.  In the Fresnel approximation we assume that $|x-x'|/D\ll 1$ and $|y-y'|/D\ll 1$, but will not assume that the aperture itself is small.  Therefore we expand in the lowest orders of $(x-x')/D$ and $(y-y')/D$ and obtain
\[  \E(P) \approx \B\frac{\exp\left(\si(kD-\omega t)\right)}{D} \iint \exp\left(\si(x'-x)^2k/2D +\si(y'-y)^2k/2D\right) \d{(x',y')}.
\]  If we combine the constant coefficient as $\E_0$ and assume a rectangular aperture of size $[x_0,x_1]\times[y_0,y_1]$, we obtain
\begin{align*}  \E(x,y) &\approx \E_0 \int_{u_0}^{u_1} \exp\left(\si\frac\pi2 u^2\right)\d{u} \int_{v_0}^{v_1} \exp\left(\si\frac\pi2 v^2\right) \d{v} \\
  &= \E_0 \left[\C(u_1)+\si\S(u_1)-\C(u_0)-\si\S(u_0)\right] \left[\C(v_1)+\si\S(v_1)-\C(v_0)-\si\S(v_0)\right]
\end{align*} where $u_k:=\sqrt{\frac2{D\lambda}}(x_k-x)$, $v_k:= \sqrt{\frac2{D\lambda}}(y_k-y)$ for $k=0,1$ \cite[Eqns.~(8.34a\&b)]{Zim08} and $\lambda=2\pi/k$ is the wave length.  The intensity near a vertical edge results as
\[  I(x):= |\E|^2 = \frac{I_0}{2} \left[\left(\frac12-\C(u_0)\right)^2+\left(\frac12-\S(u_0)\right)^2\right].
\] See also \cite[Eqn.~(8.38)]{Zim08}.  This formula is the distance along the Euler spiral between the right point at $t=\infty$ and the left point at $t=u_0$.

\FloatBarrier 
\subsection{Railway  Construction}
